State and Parameter Estimation for Spatio-Temporal Neural Fields

### 2010-05-03 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
added some figurs

\subsection{State and Parameter Estimates} To demonstrate the performance of the parameter and state estimation, $200$ realisations of the data were generated. Each realisation consisted of 300 ms of data and the estimation was applied to the final 200 ms, allowing the model to stabilise. The initial state and parameters were unknown to the estimator. The state estimates were evaluated by comparing the field reconstruction to the true field using the mean over time of the RMSE and standard deviation of the RMSE. The distribution of the state estimates are shown in figure~\ref{}.

>>>>

\subsection{State and Parameter Estimates} To demonstrate the performance of the parameter and state estimation, $200$ realisations of the data were generated. Each realisation consisted of 200 ms of data and the estimation was applied to the final 200 ms, allowing the model to stabilise. The initial state and parameters were unknown to the estimator. The state estimates were evaluated by comparing the field reconstruction to the true field using the mean over time of the RMSE and standard deviation of the RMSE. The distribution of the parameters and the resulting kernel are shown in figure~\ref{fig:Parameters} and figure~\ref{fig:KernelEstimates} respectively.
\begin{figure}
\includegraphics[width=0.5\textwidth]{./Graph/KernelEstimate.pdf}
\caption{Mean kernel estimates over 272 runs ;  true and estimated kernels are shown by solid
and dashed line respectively, the red area shows 95\% confedence interval.}
\label{fig:KernelEstimates}
\end{figure}
